### 2015-05-14 background.tex
fixes

The most common method for avoiding races is to protecting sets of program statements that access a shared resource using \emph{locks}, forming \emph{critical sections}.  
Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the races in Figure~\ref{fig:data_race_example}. Because the return statement can potentially race on the \texttt{f\_pos} field, we store the result in a temporary variable inside the critical section.
%
Careless use of locks has many pitfalls~\cite{sutter2005software}: coarse-grained locking can hurt performance, as it limits the opportunity for concurrency, while fine-grained locking can easily lead to deadlocks. Although the Linux kernel provides sophisticated lock-free synchronization mechanisms~\cite{corbet2005linux}, such as atomic read-modify-write operations, in this work we focus on locks as they are widely used.\footnote{We treat lock-free operations soundly by not regarding them as providing any protection between threads, but this can lead to false alarm race reports.}

>>>>

The most common method for avoiding races is by protecting sets of program statements that access a shared resource using \emph{locks}, forming \emph{critical sections}.  Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the races in Figure~\ref{fig:data_race_example}. Because the return statement can potentially race on the \texttt{f\_pos} field, we store the result in a temporary variable inside the critical section.
%
Careless use of locks has many well-known pitfalls~\cite{sutter2005software}: coarse-grained locking can hurt performance, as it limits the opportunity for concurrency; while fine-grained locking can easily lead to deadlocks. Although the Linux kernel provides sophisticated lock-free synchronization mechanisms~\cite{corbet2005linux}, such as atomic read-modify-write operations, in this work we focus on locks as they are widely used.\footnote{We treat lock-free operations soundly, by not regarding them as providing any protection between threads, but this can lead to false alarm race reports.}

### 2015-05-14 related.tex
fixes

Statically race analysis is a promising alternative to dynamic techniques, which restrict analysis to the schedule chosen by a (possibly controlled) scheduler, providing limited coverage~\cite{musuvathi2008finding}. Warlock~\cite{sterling1993warlock} and LockLint~\cite{oracle2010locklint} are notable static race analyzers.  In comparison to \whoop, these tools rely heavily on user annotations.

>>>>

Static race analysis is a promising alternative to dynamic techniques, which restrict analysis to the schedule chosen by a (possibly controlled) scheduler, providing limited coverage~\cite{musuvathi2008finding}. Warlock~\cite{sterling1993warlock} and LockLint~\cite{oracle2010locklint} are notable static race analyzers.  In comparison to \whoop, these tools rely heavily on user annotations.
